### 2024-08-27 paper-reviews/papers-2024.tex
Add a paper about linguistic regularities in word representation

    The paper described dropout training approach aimed to prevent co-adaptation between several feature detectors within a network. The co-adaptation often leads to overfitting of the network. This problem is greatly reduced by randomly omitting results of some (half in the paper) feature detectors. The dropout ensures that each neuron learns to detect a feature in isolation that is in turn improves network's performance as demonstrated by the paper.
\end{itemize}

>>>>

    The paper described dropout training approach aimed to prevent co-adaptation between several feature detectors within a network. The co-adaptation often leads to overfitting of the network. This problem is greatly reduced by randomly omitting results of some (half in the paper) feature detectors. The dropout ensures that each neuron learns to detect a feature in isolation that is in turn improves network's performance as demonstrated by the paper.

    \item \cite{Mikolov:LinguisticRI:2013}:

    The paper examines how linguistic regularities are present in vector-space word representations implicitly learned by language models. The words are represented as high dimensional real valued vectors. The study shows that syntactic and semantic language regularities (male/female, singular/plural, etc.) are characterized by a relation-specific vector offset. The authors showed that it is possible to use the regularities to answers analogy questions.
\end{itemize}
